% !TEX program = xelatex
\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.35cm]{geometry}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}

\setmainfont{Times New Roman}
\setsansfont{Helvetica}

\hypersetup{colorlinks=true,urlcolor=blue,linkcolor=blue}

\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=1pt}
% (titlesec spacing/format removed to avoid hidden-character parse issues)
\definecolor{cvgray}{HTML}{444444}
\newcommand{\cvsection}[1]{\vspace{2pt}\noindent\textbf{\large #1}\\[-2pt]\textcolor{cvgray}{\rule{\linewidth}{0.4pt}}\vspace{2pt}}


\newcommand{\cvname}[1]{{\huge\textbf{#1}}}
\newcommand{\cvsubheading}[2]{\textbf{#1} \hfill {#2}\\}
\newcommand{\cvsmall}{\fontsize{10.5pt}{13pt}\selectfont}
\newcommand{\cvitem}[2]{\textbf{#1}\hfill \textcolor{cvgray}{#2}\\}

\begin{document}
\cvsmall

\begin{tabularx}{\linewidth}{@{}X r@{}}
\cvname{Wu Hongfan} & \textcolor{cvgray}{Academic CV (2 pages)}\\[-1pt]
\href{mailto:wuhongfan0612@foxmail.com}{wuhongfan0612@foxmail.com} & +86-13268672769\\
\end{tabularx}

\vspace{6pt}

\cvsection{Research Interests}
Distributed LLM/MoE inference systems; online stochastic control and queueing; topology-aware routing and communication optimization; spatial matching and marketplace design.

\cvsection{Education}
\cvitem{Hong Kong University of Science and Technology (HKUST)}{Aug 2023 -- Jun 2027 (expected)}
Ph.D. in Industrial Engineering and Decision Analytics

\cvitem{Nanyang Technological University (NTU)}{Aug 2022 -- Jun 2023}
M.Eng. in Computer Control and Automation \hfill GPA: 4.36/5.00

\cvitem{Huazhong University of Science and Technology (HUST)}{Sep 2018 -- Jun 2022}
B.Eng. in Electrical Engineering and Automation \hfill GPA: 3.81/4.00

\cvsection{Publications \& Working Papers}
\begin{itemize}
  \item \textbf{Spatial Matching with Heterogeneous Demand: Coordinated Key Matching Indices for Ride-Hailing} (submitted), \emph{Operations Research}.\\
  \emph{(with Sirui Wang, Jiheng Zhang)}.
  \begin{itemize}
    \item Model: two demand classes sharing drivers; endogenous pickup times via Cobb--Douglas spatial matching; two-stage customer loss (pre-match abandonment and post-match cancellation).
    \item Theory: derive per-class \emph{Key Matching Indices (KMI)} with decomposition into abandonment reduction, direct opportunity cost, and cross-market externality; optimal thresholds characterized by $(\zeta_1,\zeta_2)=(1,1)$.
    \item Algorithm: Jacobian-based coordinated Newton controller; robust convergence from arbitrary initial thresholds in numerical experiments; quantify welfare--revenue divergence under congestion.
  \end{itemize}

  \item \textbf{Airline Cargo Transport Recovery} (working paper).
  \begin{itemize}
    \item Model disrupted cargo as a backlog-clearing problem with stochastic residual bellyhold capacities; allow direct vs. transfer routing with random transfer delay.
    \item Develop time-threshold segmentation policies that trade off waiting cost against transfer time; analyze static vs. dynamic decision gaps.
  \end{itemize}

  \item \textbf{PriceMoE: Shadow-Price-Based Dynamic Routing for MoE Serving} (working paper).
  \begin{itemize}
    \item Formulate MoE routing as network utility maximization with capacity constraints; use fluid limits for tractable analysis.
    \item Interpret queue lengths / dual variables as shadow prices; resulting top-$k$ routing trades off semantic score vs. congestion price.
  \end{itemize}

  \item \textbf{Fluid-Affinity: Locality-Aware Token Routing for Distributed MoE Inference via Online Stochastic Control} (working paper).
  \begin{itemize}
    \item Online control for token routing across GPUs with transition (communication) costs; incorporate temporal locality via an affinity reward.
    \item Derive Lyapunov drift-plus-penalty controller with $[O(1/V),O(V)]$ optimality gap vs. average queue length tradeoff.
  \end{itemize}

  \item \textbf{Topology-aware MoE Routing via Two-stage Re-rank} (paper-ready draft).
  \begin{itemize}
    \item Two-stage routing with a semantic candidate constraint (top-$M$) and topology-aware within-candidate re-ranking (communication cost + load guard).
    \item Targets multi-node prefill-heavy regimes to reduce cross-node bytes and stabilize tail latency; connects to OR online control viewpoints.
  \end{itemize}
\end{itemize}

\cvsection{Research Summary (Selected Themes)}
\begin{itemize}
  \item \textbf{Online control in coupled systems:} index/threshold policies, Jacobian-based coordination, and Lyapunov drift analysis.
  \item \textbf{Fluid/steady-state approximations:} tractable limits for optimization/design in spatial matching and distributed inference.
  \item \textbf{Interpretable decision rules:} shadow prices and decompositions that expose externalities and congestion costs.
\end{itemize}

\cvsection{Research \& Project Experience}
\cvitem{CARTIN Lab, NTU (Student Assistant)}{Dec 2022 -- Apr 2023}
Student Assistant --- Shuttle bus data visualization system (Sentosa)\\[-2pt]
\begin{itemize}
  \item Built backend/database for real-time visualization of shuttle bus location and passenger boarding/alighting statistics.
\end{itemize}

\cvitem{IoT Distributed Home Monitoring \& Security System (Team Lead)}{May 2020 -- May 2021}
\begin{itemize}
  \item Team lead; designed end-to-end IoT architecture and implemented prototypes with microcontroller-based sensing, firmware, and hardware assembly.
\end{itemize}

\cvsection{Service \& Additional Activities}
\begin{itemize}
  \item Student assistantship and project delivery in applied mobility analytics (NTU CARTIN Lab).
  \item Prior hardware/embedded prototyping experience (STM32/MCU-based control; IoT sensing).
\end{itemize}

\cvsection{Selected Technical Skills}
\begin{itemize}
  \item \textbf{Modeling/OR:} queueing networks, spatial matching, stochastic control, constrained optimization, fluid limits
  \item \textbf{Implementation:} Python for simulation/experiments; SQL (MySQL); MATLAB; C/C++
\end{itemize}

\cvsection{Skills}
\textbf{Programming:} Python, C/C++, MATLAB, SQL (MySQL)\\
\textbf{Systems/Tools:} ARM Keil, PSIM, COMSOL\\
\textbf{Languages:} Chinese (native, PSC Grade 2A); English (IELTS 7; CET-6 572)

\cvsection{Honors \& Awards}
\begin{itemize}
  \item Outstanding Graduate, HUST
  \item Innovation of Science and Technology Scholarship; Study Scholarship
  \item Interdisciplinary Contest in Modeling (ICM): Honorable Mention (H Prize)
  \item Excellence Award, \emph{Qiushi Cup} Entrepreneurship Contest ("The Flash" EV charging service app)
  \item Outstanding Volunteer, Youth Reading Challenges (Forbes World Record, Asia \& Pacific Area)
\end{itemize}

\end{document}
